---
title: "qa-files-metadata"
author: "Andrea Seisler"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Now compare .csv filenames to filenames shared in OneDrive

# 0. Required Libraries

```{r}
library(dplyr)
library(databraryr)
library(compareDF)
library(stringr)
```

# 2. Read Metadata File
```{r }
metadata <- read.csv("~/Documents/spencer-curation/ALPS-demographics-2023-05-31v01.csv")
metadata.all.df <- as.data.frame(metadata)

# Select Required Columns Only
metadata.required.df <- dplyr::select(metadata.all.df, Audio_sample.mp3,Oral_Transcribed_sample.txt, Written_Transcribed_Sample_As.Written.txt,  Written_Transcribed_Sample_Interpretted.txt, PDF_written.pdf)

#Convert DF to a single list
metadata.list <- unlist(metadata.required.df, use.names = FALSE)

# remove "" from list
metadata.list <- as.character(metadata.list[metadata.list!=""])
```

# 3.  Read uploaded data files (e.g. .mp3/.txt/.pdf) and Compare to metadata list
```{r}
source("~/Documents/R/db-data-upload-qa/id_missing.R")

missing.files <- purrr::map2(rep(c("EGO", "EGW", "ERO", "ERW", "NGO", "NGW", "NRO", "NRW"),4), rep(c("K","1","2","3"),8),id_missing)

#purrr::list_rbind(missing.files$comparison_df)

```

# 4. Print Missing Files to Screen
# Ultimately I want to export the list of files to a .csv
```{r}
for (i in 1:32){
  print(missing.files[[i]][["comparison_df"]])
}
```

#purrr::list_rbind(missing.files[[i]][["comparison_df"]])

#write.csv(this.df, "~/Documents/spencer-curation/missingFiles-", i, ".csv")

# 5. Print all missing files to output file

```{r}
all.missing.files = data.frame()
for (i in 1:32){
  temp.missing.files <- as.data.frame(missing.files[[i]][["comparison_df"]])
  all.missing.files <- rbind(all.missing.files,temp.missing.files)
}

write.csv(all.missing.files, "~/Documents/spencer-curation/missingFiles.csv")

```


# - means On OneDrive/Databrary, NOT in .csv file
# + means in .csv file, NOT on OneDrive/Databrary


